\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\usepackage{enumitem}

\title{Implementation Plan: MySQL DR (Click \& Pleniged)}
\author{Disaster Recovery Project Team}
\date{\today}

\begin{document}

\maketitle

\section{Overview}
This document outlines the step-by-step implementation for the Disaster Recovery (DR) architecture concerning the \textbf{Click} and \textbf{Pleniged} MySQL environments. It breaks down the prerequisites, current infrastructure, and executable tasks suitable for Jira import.

\section{What We Have}
\textbf{Production Environment (Zone 0):}
\begin{itemize}
    \item \textbf{Click}: MySQL 8.0 running on Ubuntu Linux (32 GB RAM, 16 vCPUs, DB Size: 0.1 GB).
    \item \textbf{Pleniged DB}: MySQL 8.0 running on Windows (32 GB RAM, 16 vCPUs, DB Size: $\sim$32 GB).
    \item \textbf{Pleniged FS}: File system containing images and PDFs ($\sim$4 TB).
    \item \textbf{Monitoring}: Observability tools including Prometheus and Grafana.
\end{itemize}

\section{What We Need}
\textbf{Disaster Recovery Environment (Target):}
\begin{itemize}
    \item \textbf{DR VMs}: Allocation of target virtual machines mirroring production specs (Ubuntu for Click, Windows for Pleniged).
    \item \textbf{Network rules}: Firewall configurations allowing TCP 3306 (MySQL) and SSH/Rsync (Port 22/TCP).
    \item \textbf{Deployment Software}: Percona XtraBackup (for binary hot backups) and Rsync (for Pleniged file system sync).
    \item \textbf{Replication}: MySQL Semi-Synchronous replication enabling Primary to DR syncing.
\end{itemize}

\section{Jira Epics and Tasks}
Here is the granular breakdown of tasks that can be bulk-imported into Jira for the engineering team.

\subsection{Epic 1: DR Infrastructure Preparation}
\begin{itemize}[label=$\square$]
    \item \textbf{Task 1.1}: Provision DR Virtual Machine for \textbf{Click} (Ubuntu Linux, 32 GB RAM, 16 vCPUs). (Assignee: Ahmed Abd Dayem Ahmed Bouha)
    \item \textbf{Task 1.2}: Provision DR Virtual Machine for \textbf{Pleniged} (Windows, 32 GB RAM, 16 vCPUs). (Assignee: Ahmed Abd Dayem Ahmed Bouha)
    \item \textbf{Task 1.3}: Configure Network and Firewall to allow TCP 3306 (MySQL) from Primary to DR VMs. (Assignee: Ahmed Abd Dayem Ahmed Bouha)
    \item \textbf{Task 1.4}: Configure Network and Firewall to allow SSH/Rsync traffic for Pleniged FS. (Assignee: Ahmed Abd Dayem Ahmed Bouha)
\end{itemize}

\subsection{Epic 2: Click Environment DR Setup (Ubuntu/MySQL)}
\begin{itemize}[label=$\square$]
    \item \textbf{Task 2.1}: Install MySQL 8.0 on the Click DR virtual machine. (Assignee: Ahmed Abd Dayem Ahmed Bouha)
    \item \textbf{Task 2.2}: Install Percona XtraBackup on Click Primary and DR VMs. (Assignee: Ahmed Abd Dayem Ahmed Bouha)
    \item \textbf{Task 2.3}: Execute preliminary full backup on Primary using XtraBackup and restore on DR VM. (Assignee: Ahmed Abd Dayem Ahmed Bouha)
    \item \textbf{Task 2.4}: Configure and enable MySQL Semi-Synchronous Replication from Primary to DR. (Assignee: Ahmed Abd Dayem Ahmed Bouha)
    \item \textbf{Task 2.5}: Verify Replication status, sync gaps, and replication delay (RPO check). (Assignee: Ahmed Abd Dayem Ahmed Bouha)
\end{itemize}

\subsection{Epic 3: Pleniged Environment DR Setup (Windows/MySQL)}
\begin{itemize}[label=$\square$]
    \item \textbf{Task 3.1}: Install MySQL 8.0 on the Pleniged DR virtual machine. (Assignee: Ahmed Abd Dayem Ahmed Bouha)
    \item \textbf{Task 3.2}: Configure Percona XtraBackup (or verified Windows-compatible tool) on Pleniged Primary. (Assignee: Ahmed Abd Dayem Ahmed Bouha)
    \item \textbf{Task 3.3}: Perform initial database backup from Primary and restore to Pleniged DR. (Assignee: Ahmed Abd Dayem Ahmed Bouha)
    \item \textbf{Task 3.4}: Configure and enable MySQL Semi-Synchronous Replication from Primary to DR. (Assignee: Ahmed Abd Dayem Ahmed Bouha)
    \item \textbf{Task 3.5}: Set up scheduled nightly Rsync job for the Pleniged FS (4 TB). (Assignee: Ahmed Abd Dayem Ahmed Bouha)
    \item \textbf{Task 3.6}: Verify replication status and Rsync nighttime job completion logs. (Assignee: Ahmed Abd Dayem Ahmed Bouha)
\end{itemize}

\subsection{Epic 4: Testing \& Handover}
\begin{itemize}[label=$\square$]
    \item \textbf{Task 4.1}: Perform a DR failover and fallback test for the Click environment. (Assignee: Ahmed Abd Dayem Ahmed Bouha)
    \item \textbf{Task 4.2}: Perform a DR failover and fallback test for the Pleniged database and File System. (Assignee: Ahmed Abd Dayem Ahmed Bouha)
    \item \textbf{Task 4.3}: Integrate DR VMs and replication status into Prometheus and Grafana alerting. (Assignee: Ahmed Abd Dayem Ahmed Bouha)
    \item \textbf{Task 4.4}: Conduct final review, secure sign-off from Team Lead, and update internal runbooks. (Assignee: Ahmed Abd Dayem Ahmed Bouha)
\end{itemize}

\end{document}
